---
title: "Finance Analytics Project"
author: "Yashdeep"
date: "23/04/2020"
output:
  word_document: default
  pdf_document: default
---

## Setup root directory for R Markdown

```{r setup}
knitr::opts_knit$set(root.dir = 'C:/Users/Hp/Desktop/R Programming')
```

## Environment Setup

```{r}
setwd("C:/Users/Hp/Desktop/R Programming")
getwd()
```

## Invoke Libraries

```{r}
library(readxl)
library(ggplot2)
library(corrplot)
library(Hmisc)
library(data.table)
library(dplyr)
library(lmtest)
library(pscl)
library(rms)
library(ROCR)
library(pROC)
```

## Data Import

```{r}
TrainData <- read_excel("raw-data.xlsx" )
TrainData <- as.data.frame(TrainData)
attach(TrainData)
TestData <- read_excel("validation_data.xlsx")
```

## Creating Dependent Variable

```{r}
TrainData$Default <- factor(ifelse(`Networth Next Year` > 0, "No" , "Yes"))
summary(TrainData$Default)
TestData$Default <- as.factor(TestData$`Default - 1`)
```

## Cleaning Train and Test Data (Removing Variables with significant NA values - Criteria: More than 40% NA's) 

```{r}
TrainData$`Deposits (accepted by commercial banks)` <- NULL
TrainData$Num <- NULL
TrainData$`Income from financial services` <-  NULL
TrainData$`Other income` <- NULL
TrainData$`Deferred tax liability` <- NULL
TrainData$`Contingent liabilities` <- NULL
TrainData$Investments <- NULL
TrainData$`PE on BSE` <- NULL 
TrainData$`Equity face value` <- NULL
TrainData$`Shares outstanding` <- NULL 
TrainData$`WIP turnover` <- NULL 
TrainData$`Finished goods turnover` <- NULL

TestData$`Deposits (accepted by commercial banks)` <- NULL
TestData$Num <- NULL
TestData$`Income from financial services` <-  NULL
TestData$`Other income` <- NULL
TestData$`Deferred tax liability` <- NULL
TestData$`Contingent liabilities` <- NULL
TestData$Investments <- NULL
TestData$`PE on BSE` <- NULL 
TestData$`Equity face value` <- NULL
TestData$`Shares outstanding` <- NULL 
TestData$`WIP turnover` <- NULL 
TestData$`Finished goods turnover` <- NULL
```

## Changing class of variable to relevant data type

```{r}
sapply(TrainData, class)
TrainData[,35:37] <- sapply(TrainData[,35:37], as.numeric)
```

## Removing NA values from Train Dataset

```{r}
summary(TrainData$`Total income`[TrainData$Default == "Yes"])
summary(TrainData$`Total income`[TrainData$Default == "No"])

TrainData$`Total income`[is.na(TrainData$`Total income`) & TrainData$Default == "Yes"] =
  median(TrainData$`Total income`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Total income`[is.na(TrainData$`Total income`) & TrainData$Default == "No"] = 
  median(TrainData$`Total income`[TrainData$Default == "No"], na.rm = T) 

TrainData$`Change in stock`[is.na(TrainData$`Change in stock`)] <- median(TrainData$`Change in stock`, na.rm = T)
summary(TrainData$`Change in stock`)

summary(TrainData$`Total expenses`[TrainData$Default == "Yes"])
summary(TrainData$`Total expenses`[TrainData$Default == "No"])

TrainData$`Total expenses`[is.na(TrainData$`Total expenses`) & TrainData$Default == "Yes"] =
  median(TrainData$`Total expenses`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Total expenses`[is.na(TrainData$`Total expenses`) & TrainData$Default == "No"] = 
  median(TrainData$`Total expenses`[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$`Profit after tax`[TrainData$Default == "Yes"])
summary(TrainData$`Profit after tax`[TrainData$Default == "No"])

TrainData$`Profit after tax`[is.na(TrainData$`Profit after tax`) & TrainData$Default == "Yes"] =
  median(TrainData$`Profit after tax`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Profit after tax`[is.na(TrainData$`Profit after tax`) & TrainData$Default == "No"] = 
  median(TrainData$`Profit after tax`[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$PBDITA[TrainData$Default == "Yes"])
summary(TrainData$PBDITA[TrainData$Default == "No"])

TrainData$PBDITA[is.na(TrainData$PBDITA) & TrainData$Default == "Yes"] =
  median(TrainData$PBDITA[TrainData$Default == "Yes"], na.rm = T)

TrainData$PBDITA[is.na(TrainData$PBDITA) & TrainData$Default == "No"] = 
  median(TrainData$PBDITA[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$PBT[TrainData$Default == "Yes"])
summary(TrainData$PBT[TrainData$Default == "No"])

TrainData$PBT[is.na(TrainData$PBT) & TrainData$Default == "Yes"] =
  median(TrainData$PBT[TrainData$Default == "Yes"], na.rm = T)

TrainData$PBT[is.na(TrainData$PBT) & TrainData$Default == "No"] = 
  median(TrainData$PBT[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$`Cash profit`[TrainData$Default == "Yes"])
summary(TrainData$`Cash profit`[TrainData$Default == "No"])

TrainData$`Cash profit`[is.na(TrainData$`Cash profit`) & TrainData$Default == "Yes"] =
  median(TrainData$`Cash profit`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Cash profit`[is.na(TrainData$`Cash profit`) & TrainData$Default == "No"] = 
  median(TrainData$`Cash profit`[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$`PBDITA as % of total income`[TrainData$Default == "Yes"])
summary(TrainData$`PBDITA as % of total income`[TrainData$Default == "No"])

TrainData$`PBDITA as % of total income`[is.na(TrainData$`PBDITA as % of total income`) & TrainData$Default == "Yes"] =
  median(TrainData$`PBDITA as % of total income`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`PBDITA as % of total income`[is.na(TrainData$`PBDITA as % of total income`) & TrainData$Default == "No"] = 
  median(TrainData$`PBDITA as % of total income`[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$`PBT as % of total income`[TrainData$Default == "Yes"])
summary(TrainData$`PBT as % of total income`[TrainData$Default == "No"])

TrainData$`PBT as % of total income`[is.na(TrainData$`PBT as % of total income`) & TrainData$Default == "Yes"] =
  median(TrainData$`PBT as % of total income`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`PBT as % of total income`[is.na(TrainData$`PBT as % of total income`) & TrainData$Default == "No"] = 
  median(TrainData$`PBT as % of total income`[TrainData$Default == "No"], na.rm = T) 

summary(TrainData$`PAT as % of total income`[TrainData$Default == "Yes"])
summary(TrainData$`PAT as % of total income`[TrainData$Default == "No"])

TrainData$`PAT as % of total income`[is.na(TrainData$`PAT as % of total income`) & TrainData$Default == "Yes"] =
  median(TrainData$`PAT as % of total income`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`PAT as % of total income`[is.na(TrainData$`PAT as % of total income`) & TrainData$Default == "No"] = 
  median(TrainData$`PAT as % of total income`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Cash profit as % of total income`[TrainData$Default == "Yes"])
summary(TrainData$`Cash profit as % of total income`[TrainData$Default == "No"])

TrainData$`Cash profit as % of total income`[is.na(TrainData$`Cash profit as % of total income`) & TrainData$Default == "Yes"] =
  median(TrainData$`Cash profit as % of total income`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Cash profit as % of total income`[is.na(TrainData$`Cash profit as % of total income`) & TrainData$Default == "No"] = 
  median(TrainData$`Cash profit as % of total income`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$Sales[TrainData$Default == "Yes"])
summary(TrainData$Sales[TrainData$Default == "No"])

TrainData$Sales[is.na(TrainData$Sales) & TrainData$Default == "Yes"] =
  median(TrainData$Sales[TrainData$Default == "Yes"], na.rm = T)

TrainData$Sales[is.na(TrainData$Sales) & TrainData$Default == "No"] = 
  median(TrainData$Sales[TrainData$Default == "No"], na.rm = T)

TrainData$`Total capital`[is.na(TrainData$`Total capital`)] <- median(TrainData$`Total capital`, na.rm = TRUE)

summary(TrainData$`Reserves and funds`[TrainData$Default == "Yes"])
summary(TrainData$`Reserves and funds`[TrainData$Default == "No"])

TrainData$`Reserves and funds`[is.na(TrainData$`Reserves and funds`) & TrainData$Default == "Yes"] =
  median(TrainData$`Reserves and funds`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Reserves and funds`[is.na(TrainData$`Reserves and funds`) & TrainData$Default == "No"] = 
  median(TrainData$`Reserves and funds`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$Borrowings[TrainData$Default == "Yes"])
summary(TrainData$Borrowings[TrainData$Default == "No"])

TrainData$Borrowings[is.na(TrainData$Borrowings) & TrainData$Default == "Yes"] =
  median(TrainData$Borrowings[TrainData$Default == "Yes"], na.rm = T)

TrainData$Borrowings[is.na(TrainData$Borrowings) & TrainData$Default == "No"] = 
  median(TrainData$Borrowings[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Current liabilities & provisions`[TrainData$Default == "Yes"])
summary(TrainData$`Current liabilities & provisions`[TrainData$Default == "No"])

TrainData$`Current liabilities & provisions`[is.na(TrainData$`Current liabilities & provisions`) & TrainData$Default == "Yes"] =
  median(TrainData$`Current liabilities & provisions`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Current liabilities & provisions`[is.na(TrainData$`Current liabilities & provisions`) & TrainData$Default == "No"] = 
  median(TrainData$`Current liabilities & provisions`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Cumulative retained profits`[TrainData$Default == "Yes"])
summary(TrainData$`Cumulative retained profits`[TrainData$Default == "No"])

TrainData$`Cumulative retained profits`[is.na(TrainData$`Cumulative retained profits`) & TrainData$Default == "Yes"] =
  median(TrainData$`Cumulative retained profits`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Cumulative retained profits`[is.na(TrainData$`Cumulative retained profits`) & TrainData$Default == "No"] = 
  median(TrainData$`Cumulative retained profits`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Net fixed assets`[TrainData$Default == "Yes"])
summary(TrainData$`Net fixed assets`[TrainData$Default == "No"])

TrainData$`Net fixed assets`[is.na(TrainData$`Net fixed assets`) & TrainData$Default == "Yes"] =
  median(TrainData$`Net fixed assets`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Net fixed assets`[is.na(TrainData$`Net fixed assets`) & TrainData$Default == "No"] = 
  median(TrainData$`Net fixed assets`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Current assets`[TrainData$Default == "Yes"])
summary(TrainData$`Current assets`[TrainData$Default == "No"])

TrainData$`Current assets`[is.na(TrainData$`Current assets`) & TrainData$Default == "Yes"] =
  median(TrainData$`Current assets`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Current assets`[is.na(TrainData$`Current assets`) & TrainData$Default == "No"] = 
  median(TrainData$`Current assets`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Net working capital`[TrainData$Default == "Yes"])
summary(TrainData$`Net working capital`[TrainData$Default == "No"])

TrainData$`Net working capital`[is.na(TrainData$`Net working capital`) & TrainData$Default == "Yes"] =
  median(TrainData$`Net working capital`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Net working capital`[is.na(TrainData$`Net working capital`) & TrainData$Default == "No"] = 
  median(TrainData$`Net working capital`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Quick ratio (times)`[TrainData$Default == "Yes"])
summary(TrainData$`Quick ratio (times)`[TrainData$Default == "No"])

TrainData$`Quick ratio (times)`[is.na(TrainData$`Quick ratio (times)`) & TrainData$Default == "Yes"] =
  median(TrainData$`Quick ratio (times)`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Quick ratio (times)`[is.na(TrainData$`Quick ratio (times)`) & TrainData$Default == "No"] = 
  median(TrainData$`Quick ratio (times)`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Current ratio (times)`[TrainData$Default == "Yes"])
summary(TrainData$`Current ratio (times)`[TrainData$Default == "No"])

TrainData$`Current ratio (times)`[is.na(TrainData$`Current ratio (times)`) & TrainData$Default == "Yes"] =
  median(TrainData$`Current ratio (times)`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Current ratio (times)`[is.na(TrainData$`Current ratio (times)`) & TrainData$Default == "No"] = 
  median(TrainData$`Current ratio (times)`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Cash to current liabilities (times)`[TrainData$Default == "Yes"])
summary(TrainData$`Cash to current liabilities (times)`[TrainData$Default == "No"])

TrainData$`Cash to current liabilities (times)`[is.na(TrainData$`Cash to current liabilities (times)`) & TrainData$Default == "Yes"] =
  median(TrainData$`Cash to current liabilities (times)`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Cash to current liabilities (times)`[is.na(TrainData$`Cash to current liabilities (times)`) & TrainData$Default == "No"] = 
  median(TrainData$`Cash to current liabilities (times)`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Cash to average cost of sales per day`[TrainData$Default == "Yes"])
summary(TrainData$`Cash to average cost of sales per day`[TrainData$Default == "No"])

TrainData$`Cash to average cost of sales per day`[is.na(TrainData$`Cash to average cost of sales per day`) & TrainData$Default == "Yes"] =
  median(TrainData$`Cash to average cost of sales per day`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Cash to average cost of sales per day`[is.na(TrainData$`Cash to average cost of sales per day`) & TrainData$Default == "No"] = 
  median(TrainData$`Cash to average cost of sales per day`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Creditors turnover`[TrainData$Default == "Yes"])
summary(TrainData$`Creditors turnover`[TrainData$Default == "No"])

TrainData$`Creditors turnover`[is.na(TrainData$`Creditors turnover`) & TrainData$Default == "Yes"] =
  median(TrainData$`Creditors turnover`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Creditors turnover`[is.na(TrainData$`Creditors turnover`) & TrainData$Default == "No"] = 
  median(TrainData$`Creditors turnover`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Debtors turnover`[TrainData$Default == "Yes"])
summary(TrainData$`Debtors turnover`[TrainData$Default == "No"])

TrainData$`Debtors turnover`[is.na(TrainData$`Debtors turnover`) & TrainData$Default == "Yes"] =
  median(TrainData$`Debtors turnover`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Debtors turnover`[is.na(TrainData$`Debtors turnover`) & TrainData$Default == "No"] = 
  median(TrainData$`Debtors turnover`[TrainData$Default == "No"], na.rm = T)

summary(TrainData$`Raw material turnover`[TrainData$Default == "Yes"])
summary(TrainData$`Raw material turnover`[TrainData$Default == "No"])

TrainData$`Raw material turnover`[is.na(TrainData$`Raw material turnover`) & TrainData$Default == "Yes"] =
  median(TrainData$`Raw material turnover`[TrainData$Default == "Yes"], na.rm = T)

TrainData$`Raw material turnover`[is.na(TrainData$`Raw material turnover`) & TrainData$Default == "No"] = 
  median(TrainData$`Raw material turnover`[TrainData$Default == "No"], na.rm = T)
```

## Structure, Summary, Dimensions and Verifying elimated NA values

```{r}
colSums(is.na(TrainData))
sum(is.na(TrainData))
dim(TrainData)
summary(TrainData)
str(TrainData)
```

## Creating New Variable Capital as a Percentage of Assets (Company's Size)

```{r}
TrainData$Size.Ratio.CapitalAsPerc.Assets <- (TrainData$`Total capital`/TrainData$`Total assets`) *100
summary(TrainData$Size.Ratio.CapitalAsPerc.Assets)
TestData$Size.Ratio.CapitalAsPerc.Assets <- (TestData$`Total capital`/TestData$`Total assets`) *100
summary(TestData$Size.Ratio.CapitalAsPerc.Assets)
```

## Profit before depreciation, income tax and amortization as a percentage of Total Income (Profitabilty)

```{r}
TrainData$PBDITA.PERC.TotalIncome <- (TrainData$PBDITA/TrainData$`Total income`)*100
summary(TrainData$PBDITA.PERC.TotalIncome)
```

## Creating New Ratio Variable for leverage using Borrowings and Current Liabilities

```{r}
TrainData$Leverage.Ratio <- (TrainData$`Total liabilities` - TrainData$Borrowings)/`Total liabilities`
summary(TrainData$Leverage.Ratio)
TestData$Leverage.Ratio <- (TestData$`Total liabilities` - TestData$Borrowings)/TestData$`Total liabilities`
summary(TestData$Leverage.Ratio)
```

## Creating new variable for Liquidity - Net Working Capital divided by Total Liabilities

```{r}
TrainData$Liquidity.Ratio.CapitalByLiabilities <- (TrainData$`Net working capital`/TrainData$`Total liabilities`)
summary(TrainData$Liquidity.Ratio.CapitalByLiabilities)
TestData$Liquidity.Ratio.CapitalByLiabilities <- (TestData$`Net working capital`/TestData$`Total liabilities`)
summary(TestData$Liquidity.Ratio.CapitalByLiabilities)
```

## Check for Multicollinearity 

```{r}
head(TrainData)
Matrix1 <- cor(TrainData[,2:15])
Matrix2 <- cor(TrainData[,16:30])
Matrix3 <- cor(TrainData[ ,c(31:40,42,43,44,45)])
corrplot(Matrix1, method = "pie", type = "upper")
corrplot(Matrix2,method = "pie", type = "upper")
corrplot(Matrix3, method = "pie", type = "upper")
```

## Outlier Treatment for Significant Variables using flooring/capping (Variables to be used in Model)

```{r}
summary(TrainData$`Total income`)
IQRIncome = IQR(TrainData$`Total income`)
LLIncome = quantile(TrainData$`Total income`,0.25) - 1.5*IQRIncome
ULIncome = quantile(TrainData$`Total income`,0.75) + 1.5*IQRIncome
IncomeOut = subset(TrainData, `Total income` < LLIncome | `Total income` > ULIncome)
dim(IncomeOut)

IncomeWOUT = subset(TrainData, `Total income` >= LLIncome & `Total income` <= ULIncome)
dim(IncomeWOUT)
max(IncomeWOUT$`Total income`)
summary(TrainData$`Total income`)
TrainData$`Total income`[TrainData$`Total income` > 3171.7] = 3171.7
boxplot(TrainData$`Total income`, main = "Boxplot of Total Income Post Outlier Treatment", xlab = "Total Income")

summary(TrainData$`Profit after tax`)
IQRPAT = IQR(TrainData$`Profit after tax`)
LLPAT = quantile(TrainData$`Profit after tax`,0.25) - 1.5*IQRPAT
ULPAT = quantile(TrainData$`Profit after tax`,0.75) + 1.5*IQRPAT
PATOut = subset(TrainData, `Profit after tax` < LLPAT | `Profit after tax` > ULPAT)
dim(PATOut)

PATWOUT = subset(TrainData, `Profit after tax` >= LLPAT & `Profit after tax` <= ULPAT)
dim(PATWOUT)
max(PATWOUT$`Profit after tax`)
min(PATWOUT$`Profit after tax`)
summary(TrainData$`Profit after tax`)
TrainData$`Profit after tax`[TrainData$`Profit after tax` >= 119.2] = 119.2
TrainData$`Profit after tax`[TrainData$`Profit after tax` <= -70.9] = -70.9
boxplot(TrainData$`Profit after tax`, main = "Boxplot of Profit after Tax Post Outlier Treatment", xlab = "Profit after tax")

summary(TrainData$`PAT as % of net worth`)
IQRPATNW = IQR(TrainData$`PAT as % of net worth`)
LLPATNW = quantile(TrainData$`PAT as % of net worth`,0.25) - 1.5*IQRPATNW
ULPATNW = quantile(TrainData$`PAT as % of net worth`,0.75) + 1.5*IQRPATNW
PATNWOut = subset(TrainData, `PAT as % of net worth` < LLPATNW | `PAT as % of net worth` > ULPATNW)
dim(PATNWOut)

PATNWWOUT = subset(TrainData, `PAT as % of net worth` >= LLPATNW & `PAT as % of net worth` <= ULPATNW)
dim(PATNWWOUT)
max(PATWOUT$`PAT as % of net worth`)
min(PATWOUT$`PAT as % of net worth`)
summary(TrainData$`PAT as % of net worth`)
TrainData$`PAT as % of net worth`[TrainData$`PAT as % of net worth` >= 2466.67] = 2466.67
TrainData$`PAT as % of net worth`[TrainData$`PAT as % of net worth` <= -584.44] = -584.44
boxplot(TrainData$`PAT as % of net worth`, main = "Boxplot of PAT as % of net worth Post Outlier Treatment", xlab = "PAT as % of net worth")

summary(TrainData$`Debt to equity ratio (times)`)
boxplot(TrainData$`Debt to equity ratio (times)`)
IQRDTE = IQR(TrainData$`Debt to equity ratio (times)`)
LLDTE = quantile(TrainData$`Debt to equity ratio (times)`,0.25) - 1.5*IQRDTE
ULDTE = quantile(TrainData$`Debt to equity ratio (times)`,0.75) + 1.5*IQRDTE
DTEOut = subset(TrainData, `Debt to equity ratio (times)` < LLDTE | `Debt to equity ratio (times)` > ULDTE)
dim(DTEOut)

DTEWOUT = subset(TrainData, `Debt to equity ratio (times)` >= LLDTE & `Debt to equity ratio (times)` <= ULDTE)
dim(DTEWOUT)
max(DTEWOUT$`Debt to equity ratio (times)`)
summary(TrainData$`Debt to equity ratio (times)`)
TrainData$`Debt to equity ratio (times)`[TrainData$`Debt to equity ratio (times)` >= 4.04] = 4.04
boxplot(TrainData$`Debt to equity ratio (times)`,  main = "Boxplot of Debt to Equity Ratio Post Outlier Treatment", xlab = "Debt to Equity Ratio")

summary(TrainData$`Net working capital`)
boxplot(TrainData$`Net working capital`)
IQRNWC = IQR(TrainData$`Net working capital`)
LLNWC = quantile(TrainData$`Net working capital`,0.25) - 1.5*IQRNWC
ULNWC = quantile(TrainData$`Net working capital`,0.75) + 1.5*IQRNWC
NWCOut = subset(TrainData, `Net working capital` < LLNWC | `Net working capital` > ULNWC)
dim(NWCOut)

NWCWOUT = subset(TrainData, `Net working capital` >= LLNWC & `Net working capital` <= ULNWC)
dim(NWCWOUT)
max(NWCWOUT$`Net working capital`)
min(NWCWOUT$`Net working capital`)
summary(TrainData$`Net working capital`)
TrainData$`Net working capital`[TrainData$`Net working capital` >= 205.2] = 205.2
TrainData$`Net working capital`[TrainData$`Net working capital` <= -123.7] = -123.7
boxplot(TrainData$`Net working capital`, main = "Boxplot of Net Working Capital Post Outlier Treatment", xlab = "Net Working Capital")
```

## Univariate and Bivariate Analysis

```{r}
qplot(TrainData$Default, xlab = "Default", ylab = "Count", 
      main  = "Distribution of Default ", fill = TrainData$Default) + theme(plot.title = element_text(hjust = 0.5)) +  labs(fill='Default')

ggplot(TrainData, aes(x=`Profit after tax`), main  = "Density Distribution of Profit after Tax") +   geom_density() + geom_vline(aes(xintercept=mean(`Profit after tax`)),
            color="blue", linetype="dashed", size=1)

ggplot(TrainData, aes(x=`Total income`),main  = "Density Distribution of Total Income") +   geom_density() + geom_vline(aes(xintercept=mean(`Total income`)),
            color="blue", linetype="dashed", size=1)

qplot(`PAT as % of net worth`, `PAT as % of total income`, xlab = "Profit After Tax as % of Net Worth", 
      ylab = "Profit after Tax as a % of Total Income", 
      main  = "Profit After Tax as % of Net Worth V/S Profit after Tax as a % of Total Income" + 
  theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method = "lm"))

qplot(`Total income`, `Total liabilities`, xlab = "Income", 
      ylab = "Total Liabilities", 
      main  = "Relationship of Income V/S Total Liabilities") + 
  theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method = "lm")

qplot(TrainData$Leverage.Ratio, `Total liabilities`, xlab = "Leverage Ratio", 
      ylab = "Total Liabilities", 
      main  = "Relationship of Leverage Ratio V/S Total Liabilities") + 
  theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method = "lm")


qplot(Sales, `Profit after tax`, xlab = "Sales", 
      ylab = "Profit After Tax", 
      main  = "Relationship of Sales V/S Profit After Tax") + 
  theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method = "lm")

ggplot(TrainData, aes(x = Default, y = TrainData$`Total income`), ylab = "Total Income" ) + geom_boxplot() + ggtitle("Boxplot of Default against Total Income") +   theme(plot.title = element_text(hjust = 0.5))

ggplot(TrainData, aes(x = Default, y = TrainData$`Debt to equity ratio (times)`), ylab = "Debt to Equity") + geom_boxplot() + ggtitle("Boxplot of Default against Debt to Equity Ratio") + theme(plot.title = element_text(hjust = 0.5))

```

## Data Slicing

```{r}
prop.table(table(TrainData$Default))

prop.table(table(TestData$Default))
```

## Logistic Regression Model Creation

```{r}
Log.Reg.Model <- glm(Default~`Total expenses`+ PBT + `PAT as % of net worth`+`Net working capital`+`Debt to equity ratio (times)`+
                        Leverage.Ratio+ Liquidity.Ratio.CapitalByLiabilities+Size.Ratio.CapitalAsPerc.Assets,data = TrainData, family = "binomial")

summary(Log.Reg.Model)

vif(Log.Reg.Model)
```

## Model Performance Measures

```{r}
anova(Log.Reg.Model)
pR2(Log.Reg.Model)
```

## Determining Threshold for Logisitc Regression Model

```{r}
summary(Log.Reg.Model$fitted.values)
plot(Log.Reg.Model$fitted.values)
plot(TrainData$Default, Log.Reg.Model$fitted.values)
```

## Prediction and Confusion Matrix on Train Dataset

```{r}
Log.Reg.Predict <- predict(Log.Reg.Model,data = TrainData, type = "response")
M <- table(TrainData$Default,Log.Reg.Predict > 0.13)
M
```

## Model Evaluation (Error Rate, Accuracy, Sensitivity, Specificity, Precision, F Score) on Train Dataset

```{r}
Classification.error.rate.log.reg.train <- (M[1,2]+M[2,1])/nrow(TrainData)
Classification.error.rate.log.reg.train*100
Accuracy.log.reg.train <- 1 - Classification.error.rate.log.reg.train
Accuracy.log.reg.train*100

Sensitivity <- M[1,1]/(M[1,1]+M[1,2])
Sensitivity
Specificity <- M[2,2]/(M[2,1]+M[2,2]) 
Specificity
Precision <- M[1,1]/(M[1,1]+M[2,1])
Precision
FScore <- 2*((Precision*Sensitivity)/(Precision+Sensitivity))
FScore
```

## Rank Ordered Tables and K.S Statistic

```{r}
TrainData$Prob <- predict(Log.Reg.Model, data = TrainData, type = "response")

probs <- seq(0,1,length = 11 )
QS <- quantile(TrainData$Prob, probs)
TrainData$Decile <- cut(TrainData$Prob, unique(QS), include.lowest = TRUE)
TrainDT <- data.table(TrainData)
RankTable <- TrainDT[, list(Count= length(Default), Defaulters = sum(Default== "Yes"), 
                            NonDefaulters = sum(Default=="No")), by = Decile][order(-Decile)] 
RankTable$DRate <- round(RankTable$Defaulters/RankTable$Count, 4)*100
RankTable$CumDefaulters <- cumsum(RankTable$Defaulters)
RankTable$CumNonDefaulters <- cumsum(RankTable$NonDefaulters)
RankTable$CumRelDefault <- round(RankTable$Defaulters/sum(RankTable$Defaulters),4)*100
RankTable$CumRelNonDefault <- round(RankTable$NonDefaulters/sum(RankTable$NonDefaulters),4)*100
RankTable$KS <- abs(RankTable$CumRelDefault-RankTable$CumRelNonDefault)

RankTable
```

## Prediction and Confusion Matrix on Test Dataset

```{r}
Predicted.Test <- predict(Log.Reg.Model, newdata = TestData, type = "response")
M1 <- table(TestData$Default,Predicted.Test > 0.13)
M1
```

## Model Evaluation (Error Rate, Accuracy, Sensitivity, Specificity, Precision, F Score) on Test Dataset

```{r}
Classification.error.rate.log.reg.test <- (M1[1,2]+M1[2,1])/nrow(TestData)
Classification.error.rate.log.reg.test*100
Accuracy.log.reg.test <- 1 - Classification.error.rate.log.reg.test
Accuracy.log.reg.test*100

Sensitivity.Test <- M1[1,1]/(M1[1,1]+M1[1,2])
Sensitivity.Test
Specificity.Test <- M1[2,2]/(M1[2,1]+M1[2,2]) 
Specificity.Test
Precision.Test <- M1[1,1]/(M1[1,1]+M1[2,1])
Precision.Test
FScore <- 2*((Precision*Sensitivity)/(Precision+Sensitivity))
FScore
```

## Rank Ordered Tables and K.S Statistic on Test Dataset

```{r}
TestData$Prob <- predict(Log.Reg.Model, newdata = TestData, type = "response")
summary(TestData$Prob)
TestData$Prob[is.na(TestData$Prob)] = median(TestData$Prob, na.rm = TRUE)


QS1 <- quantile(TestData$Prob, probs)
TestData$Decile <- cut(TestData$Prob, unique(QS1), include.lowest = TRUE)
TestDT <- data.table(TestData)
RankTable.1 <- TestDT[, list(Count= length(Default), Defaulters = sum(Default== "Yes"), 
                            NonDefaulters = sum(Default=="No")), by = Decile][order(-Decile)] 

RankTable$DRate <- round(RankTable$Defaulters/RankTable$Count, 4)*100
RankTable$CumDefaulters <- cumsum(RankTable$Defaulters)
RankTable$CumNonDefaulters <- cumsum(RankTable$NonDefaulters)
RankTable$CumRelDefault <- round(RankTable$Defaulters/sum(RankTable$Defaulters),4)*100
RankTable$CumRelNonDefault <- round(RankTable$NonDefaulters/sum(RankTable$NonDefaulters),4)*100
RankTable$KS <- abs(RankTable$CumRelDefault-RankTable$CumRelNonDefault)

RankTable
```

